Cryptographic assurance of secrecy and fairness in voting

### 2012-12-05 paper/paper.tex
Add Delaune citation for secrecy definitions
Remove empty citation command.
Vaguely start a formal notion of privacy

We give multiple definitions of ballot secrecy in order of increasing strength:
\term{privacy}, \term{receipt-freeness}, and \term{coercion resistance}.

@@

>>>>

Delaune \cite{delaune} gives several definitions of ballot secrecy.
In order of increasing strength, they are
\term{privacy}, \term{receipt-freeness}, and \term{coercion resistance}.

@@

Privacy addresses information that is revealed by the system itself.
A system is private if a voter who wants to keep her vote secret is able to do so.
In a verifiable voting system, the system includes the verification process.
So in addition to casting a vote in private, the voter must also be able to
audit her vote without revealing its content.

More formally, we can say that an election system has private ballots
if a reasonably time-bounded attacker, having access to the public information
published by the polling authority ... \todo{}
